---
title: "practice scraping	"
author: "Oliver :)"
date: "07-11-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# installing packages

```{r libraries, warning=FALSE, message=FALSE}
library(rvest)
library(dplyr)
library(tidyr)
library(stringr)
library(janitor)
library(ggplot2)
library(lubridate)
library(tidyverse)
```


i chose task 2 and decided to scrape data from https://www.worldometers.info/world-population/denmark-population/ 


```{r website} 
#select website:)
website <- "https://www.worldometers.info/world-population/denmark-population/"
website_html <- read_html(website)
```

now we extact the data and turn it into a dataframe :)
```{r}
entire_table <- website_html %>% 
 html_nodes("table")%>%
 html_table()  
the_table <- do.call(cbind,unlist(entire_table, recursive = FALSE)) 
head(the_table) #testing to check that the dataframe works
```

now generating a graph to show that the dataframe works.
but first we have to clean up the data since there are duplicate names.
```{r df}
#cleaning up the dataset for us
df<-as.data.frame(the_table)
df1<-clean_names(df) #using janitor library to clean the data since in our dataset we have multiple cases of bad naming
#if we are to use our data for matplotlib we have to change the datatype
df1$year <- as.numeric(df1$year) #transforming our year axis from a character to numeric
df1$population <- as.numeric(gsub(",","",df1$population)) #same as above but also removing the "," that are used since it bugs out the purpose of our next thing

	
```

now that our data is cleaned up we can succesfully generate a graph, im going to use the population of Denmark to see if there are any trends in the last few years.
```{r fleet_table, echo=TRUE, include=TRUE}
ggplot(data=df1, mapping=aes(x=year, y=population)) + geom_smooth()

```
we can now see that there is an upward trend in population and our datfarame works :)
